### 2016-02-21 introduction.tex
new text

Automated test generators tend to produce many failures, which correspond to far fewer faults.  The distribution of faults in a set of failures tends to follow a strong power-law curve, where a few faults account for most failures, and many or even most faults have only 1 or 2 associated failures (even in a set of 1,000 or more test cases) \cite{PLDI13}.  Looking at all the failures to find  distinct faults is impractical.  It is also impractical to apply the iterative approach:  first, fix one fault; then re-run all test cases, knowing that the remaining failures are due to different, unfixed faults, repeating until all failures go away.  First, there may be some faults that are very difficult to fix --- a large compiler project typically has many open bugs.  As of 11/20/2015, LLVM clang had 89 bugs assigned but not resolved, some dating to 2008.  Knowing if a randomly generated test case is an instance of a known failure can be difficult, and fixing these problems is unlikely.    A research group with a novel fault-detection technique \cite{csmith,ISSTA12,ZhendongPLDI} may dump dozens of new faults on a project at once, producing more open problems.

>>>>

Automated test generators tend to produce many failures, which correspond to far fewer faults.  The distribution of faults in a set of failures tends to follow a strong power-law curve, where a few faults account for most failures, and many or even most faults have only 1 or 2 associated failures (even in a set of 1,000 or more test cases) \cite{PLDI13}.  Looking at all the failures to find  distinct faults is impractical.  It is also impractical to apply the iterative approach:  first, fix one fault; then re-run all tests, knowing that the remaining failures are due to unfixed faults, repeating until all tests pass.  However, there may be some (possibly known) faults that are very difficult to fix. As of 11/20/2015, LLVM clang had 89 bugs assigned but not resolved, some dating to 2008.  Knowing if a randomly generated test case is an instance of a known failure can be difficult, and fixing these problems is unlikely.    A research group with a novel fault-detection technique \cite{csmith,ISSTA12,ZhendongPLDI} may dump dozens of new faults on a project at once, producing more open problems.   High priority faults may be hidden by stubborn low-priority faults.
